Spectroscopic Characterization of New Er$^{3+}$ Host Crystals for Quantum Network Applications

### 2020-04-22 Draft.tex
FTIR diagrams

The signal to noise ratio on the low-noise photodiode used for PLE is better than the signal to noise ratio on the array detector for the purposes of detecting the smallest signals possible. In part this is because a single detector simply introduces less noise than 1024 detectors. This has inspired the idea of using

\begin{itemize}
\item What limits our ability to measure smaller signals with the commercial spectrometer? Why do we think Fourier transform spectroscopy could improve our ability to detect smaller signals?

\item There are other advantages as well - increased range, potentially increased resolution (with larger mirror travel), no need to focus through slit. Putting FT on the excitation side with a broad spectrum source could actually give a way to do 2D spectra over extremely wide regions.
\end{itemize}

\section{Principles of Fourier transform spectroscopy}
\begin{itemize}
\item A small diagram of how FT spectroscopy works at the simplest level, and a discussion of how data is collected and processed

@@

\section{Implementation}
\begin{itemize}
\item Optical design of our FT spectrometer

>>>>

The signal to noise ratio on the low-noise photodiode used for PLE is better than the signal to noise ratio on the array detector for the purposes of detecting the smallest signals possible. In part this is because a single detector simply introduces less noise than 1024 detectors. This has inspired the idea of using another of these low-noise photodiodes to build a Fourier transform spectrometer. This could provide several benefits over the current setup, including increased range and resolution, a higher signal to noise ratio, and no more need to focus through a slit.

% \begin{itemize}
% \item What limits our ability to measure smaller signals with the commercial spectrometer? Why do we think Fourier transform spectroscopy could improve our ability to detect smaller signals?

% \item There are other advantages as well - increased range, potentially increased resolution (with larger mirror travel), no need to focus through slit. Putting FT on the excitation side with a broad spectrum source could actually give a way to do 2D spectra over extremely wide regions.
% \end{itemize}

\section{Principles of Fourier transform spectroscopy}

The basic idea of a Fourier transform spectrometer is depicted in Figure

\begin{wrapfigure}{r}{0.5\textwidth}
  \centering
  \includegraphics[width=]

\end{wrapfigure}

\begin{itemize}
\item A small diagram of how FT spectroscopy works at the simplest level, and a discussion of how data is collected and processed

@@

\section{Implementation}

\begin{figure}[b]
  \centering
  \includegraphics[width=\textwidth]{FTIRSetupDiagram}
  \caption{Diagram of our FTIR optical design.}
  \label{fig:ftirdiagram}
\end{figure}

\begin{itemize}
\item Optical design of our FT spectrometer
